DATA 621 - Business Analytics and Data Mining

### 2020-09-22 HW2/HW2-Group2.rmd
updated data path to git

# urlRemote  = "https://raw.githubusercontent.com/"
# pathGithub = "aadler/DT621_Fall2020_Group2/master/HW1/data/"
# fileTrain   = "classification-output-data.csv"
# data = paste0(urlRemote, pathGithub, fileTrain) %>% read.csv()

data = read.csv("classification-output-data.csv")
```

>>>>

urlRemote  = "https://raw.githubusercontent.com/"
pathGithub = "aadler/DT621_Fall2020_Group2/master/HW2/"
fileTrain   = "classification-output-data.csv"
data = paste0(urlRemote, pathGithub, fileTrain) %>% read.csv()
```
